Where Do Population III Stars Form?

### 2018-10-02 paper.tex
adding rough introduction -- need to add sources and further details about previous work

\medskip
\noindent Here are some bullet points to guide the intro's narrative.

\li The first generation of stars transformed a cold and dark universe
by illuminating and enriching up their neighborhoods with radiation
and heavy elements.

\li They are metal-free (Population III; Pop III) and are thought to
be generally massive and thus a substantial fraction will generate
prodigious amounts of ionizing photons and will end their lives in
supernovae \citep[e.g.][]{Schaerer02, Heger02}.

\li Once a halo becomes chemically enriched, by definition, it cannot
form Pop III stars anymore, marking the end of metal-free star
formation in that pregalactic object.  Numerical studies have shown
that turbulence within halos can mix metals well down to their
resolution limit \citep[][and more]{Wise08_Gal, Greif10}.

\li Given the paradigm of hierarchical structure formation, halos grow
through smooth accretion and successive mergers of smaller halos.  But
in which halos do these first generations of stars form?  Their
formation rates and locations are important to constrain because they
influence the very beginnings of galaxy formation and cosmic
reionization.

\li Without metals and dust to facilitate efficient radiative cooling,
Pop III stars rely on \hh{} formation to cool the gas.  These
molecules are however fragile to dissociation from Lyman-Werner
(LW) radiation in the energy range 11.2--13.6~eV.

\li Diffuse gas is optically thin to LW radiation, thus a background
builds over time and can suppress \hh{} formation and thus Pop III
star formation.  Furthermore, nearby sources of LW radiation can
dissociate \hh{} in minihalos.

\li Other sources of the suppression of Pop III star formation are
streaming baryonic velocities, arising from recombination, and
dynamical heating, occuring during the virialization of halos.

\li Previous work have mainly investigated and established the lower
limit for a halo to host Pop III stars.  However, subsequent
simulations have shown that they don't necessarily form at this
minimum, whereas other physical processes (mentioned above) play a
role.

\li In this paper, we focus on the distribution of host halo masses,
not just the minimum, and its dependence on redshift and the LW
background, augmenting the results from prior work.

\medskip
\noindent Include the ``typical'' overview of the paper's sections
last in the introduction.

>>>>

\medskip

The first generation of stars transformed a cold and dark universe
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments is necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive. A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across it's local environment, providing the area with chemicals the universe has not yet seen.

Once a halo becomes chemically enriched by the death of it's Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}. Stars will continue to form in halos, but with an increase metal abundance, these stars are now labelled as Population II, or Pop II, stars. Pop II stars are considered metal-poor, relative to their metal-free Pop III progenitors, and are observable in the universe. Understanding the formation and chemical abundance of Pop II stars can provide more evidence and insight for the earlier generation of Pop III stars.

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars.
Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation to cool the gas. These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Soloman process :
\begin{equation}
	H_{2} + \gamma \rightarrow  H + H
\end{equation}
Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, prohibiting Pop III star formation. Furthermore, nearby sources of LW radiation can dissociate \hh{} in minihalos. This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding. Halos with an \hh{} column density of N$_{H_{2}}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons, giving the halo a chance to form Pop III stars. Other sources of the suppression of Pop III star formation are streaming baryonic velocities, arising from recombination, and dynamical heating, occuring during the virialization of halos.

Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse. However, subsequent simulations have shown that they don't necessarily form at this minimum due to other physical processes (mentioned above) playing a role.

In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background, augmenting results from prior work. We aim to provide further insight into the host halos of Pop III stars. In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding is described. In \S 3 we present the results of our analysis. In \S 4 we discuss the results in more detail and compare with previous work. In \S 5 we conclude our discussion with a summary of our results and the implications therein.
